Table 1

### 2017-09-27 doc/RMD/table-1.Rmd
update table S1 to work with new huxtable

dt <- huxtable::as_huxtable(dat, add_colnames = TRUE) %>% # Creating the huxtable
  set_align(everywhere, col = 4, value = "right") %>%     # Aligning numeric columns to the right
  set_align(everywhere, col = 6, value = "right") %>%     # 
  set_wrap(TRUE) %>%                                      # Wrapping columns
  set_number_format(value = 0)                            # Print numbers without decimals
col_width(dt) <- c(0.055, 0.035, 0.06, 0.1, 0.151, 0.025) # Specify width for each column
print_md(dt)                                              # print in pandoc markdown format
```

>>>>

dt <- huxtable::as_huxtable(dat, add_colnames = TRUE) %>% # Creating the huxtable
  set_align(everywhere, col = 4, value = "right") %>%     # Aligning numeric columns to the right
  set_align(everywhere, col = 6, value = "right") %>%     # 
  # set_wrap(TRUE) %>%                                      # Wrapping columns
  set_number_format(value = 0) %>%                        # Print numbers without decimals
  set_col_width(c(0.055, 0.035, 0.06, 0.1, 0.151, 0.025)) %>% # Specify width for each column
  print_md(max_width = 80)                                # print in pandoc markdown format
```
